---
title: "EDXStats_ch3"
output: html_document
---

## CHAPTER 3: Linear Regression

```{r setup, include=FALSE}
library(MASS)
library(ISLR)
names(Boston)
?Boston
```

## Plot Median Housing Value vs Population

```{r cars}
plot(medv~lstat, Boston)
```

## Fit a Linear Model

```{r}
fit1=lm(medv~lstat, data=Boston)
```

## Summary of Linear Model

```{r}
summary(fit1)
```



You get the coefficients, their standard errors, t-values, and p-values.

And both of these are very significant.

We're typically not interested too much in the intercept.

It's the coefficient of lstat that we're interested in here.

And it's negative, and very significantly so.

```{r}
plot(medv~lstat, data=Boston)
fit1=lm(medv~lstat, data=Boston)
abline(fit1, col="red")
```
## Names

```{r}
names(fit1)
```

## Confidence Intervals

```{r}
confint(fit1)
```

## Predictions

```{r}
predict(fit1, data.frame(lstat=c(5,10,15)), interval="confidence")
```

## Multiple Linear Regression

### WITH TWO!

```{r}
fit2 = lm(medv~lstat+age, data=Boston)
summary(fit2)
```

## R Squared: The higher the better 
(A percentage of teh variance explained)

### WITH ALL!

```{r}
fit3 = lm(medv~., data=Boston)
summary(fit3)
```

```{r}
par(mfrow=c(2,2))
plot(fit3)

```

### Now remove things from fit3

```{r}
fit4=update(fit3, ~.-age-indus)
summary(fit4)
```

## Nonlinear terms and interactions
 
```{r}
# Here '*' means interaction, not product
fit5=lm(medv~lstat*age,Boston)
summary(fit5)
```

```{r}
fit6=lm(medv~lstat + I(lstat^2), Boston); summary(fit6)
```
```{r}
fit6=lm(medv~lstat + I(lstat^2), Boston); summary(fit6)
attach(Boston)
par(mfrow=c(1,1))
plot(medv~lstat, Boston)
points(lstat,fitted(fit6),col="red", pch=20)
plot(medv~lstat, Boston)
fit7=lm(medv~poly(lstat,4), Boston)
points(lstat,fitted(fit7),col="blue", pch=20)
# fit7=lm(medv~poly(lstat,4))
```

## Plotting Characters

```{r}
plot(1:20,1:20, pch=1:20, cex=2)

```

# Qualitative Predictors

```{r}
# library(Carseats)
# fix(Carseats)
names(Carseats)
```
```{r}
summary(Carseats)
```

```{r}
fit1=lm(Sales~.+Income:Advertising+Age:Price,Carseats)
summary(fit1)
# How R codes quantative variables
contrasts(Carseats$ShelveLoc)
```

## Writing R Functions

```{r}
regplot=function(x,y){
  fit=lm(y~x)
  plot(x,y)
  abline(fit,col="red")
}

attach(Carseats)
regplot(Price, Sales)

```

## Another way to write functions (WITH MORE PARAMS!)

```{r}
regplot=function(x,y,...) {
  fit=lm(y~x)
  plot(x,y,...)
  abline(fit,col="red")
}

regplot(Price,Sales, xlab="Price", ylab="Sales", col="blue", pch=20)
```




FIN. 