---
title: "EDXStats_ch5_R"
output: html_document
---

# LEAVE-ONE-OUT CROSS VALIDATION (LOOCV)

glm = generalized linear models

```{r}
require(ISLR)
require(boot)
```

## USE SUMMARY TO FIND STD.ERROR ETC.

```{r}
load("Documents/EDXStats/5.R.RData")
glm.fit=glm(y~X1+X2, data=Xy)

summary(glm.fit)
```

## BOOTSTRAPPING

So the bootstrap gives us a really easy way of doing
statistics when the theory is very hard.

And to illustrate it we'll use the example we used in the
book in section 5.2 where we have a particularly non-linear
formula for **picking an optimal combination of two
investments.**

RISK for investment X is VAR(X)
RISK for investment Y is VAR(Y)

```{r}
alpha=function(x,y){
  vx=var(x)
  vy=var(y)
  cxy=cov(x,y)
  (vy-cxy)/(vx+vy-2*cxy)
}
alpha(Portfolio$X,Portfolio$Y)

```

OK, so in order to use the bootstrap function we need to
make a little wrapper that allows a bootstrap to work.
And this is this function we'll call alpha.fn.
And what it does is it takes a data frame and an index, which
indexes rows of the data frame, and then computes your
statistic--
in this case alpha index, for which it wants to compute the
variance in this case, the standard error.

```{r}
alpha.fn=function(data, index){
  # WITH function -- using this dataframe, perform this function
  with(data[index,],alpha(X,Y))
}

alpha.fn(Portfolio,1:100)
```

NOW we run the bootstrap

```{r}
alpha.fn(Portfolio,1:100)
set.seed(1)
alpha.fn (Portfolio,sample(1:100,100,replace=TRUE))

# 1000 bootstraps
boot.out=boot(Portfolio, alpha.fn,R=1000)
boot.out
plot(boot.out)
```

So there's a bootstrap.
Very handy way of getting very good reliable estimates of
standard error for nasty statistics.


## QUIZ QUESTIONS:

```{r}
load("Documents/EDXStats/5.R.RData")
alpha.fn(Portfolio,1:100)
set.seed(1)
alpha.fn (Portfolio,sample(1:100,100,replace=TRUE))

# 1000 bootstraps
boot.out=boot(Portfolio, alpha.fn,R=1000)
boot.out
plot(boot.out)
```


FIN.
