---
title: "EDXStats_ch5_LAB"
output: html_document
---

# 5.3 LAB: Cross-Validation and the Booststrap

## 5.3.1 The Validation Set Approach

1. load library
2. set seed (so we can replicate)
3. split data into test and train

```{r}
library(ISLR)
set.seed(1)
train=sample(392,196) 
```

4. use `subset` option in `lm()` to fit a linear regression with only training set

```{r}
lm.fit=lm(mpg~horsepower, data=Auto, subset=train)
```

5. use `predict` to estimate response for all 392 observations
6. use `mean` to calculate the MSE of the 196 observations in the validation set
NOTE: `-train` selects only the observations that are not in the training set

```{r}
attach(Auto)
mean((mpg-predict(lm.fit,Auto))[-train]^2)
```

7. Quadratic and Cubic regressions

```{r}
lm.fit2=lm(mpg~poly(horsepower,2), data=Auto, subset=train)
mean((mpg-predict(lm.fit2,Auto))[-train]^2)
```

```{r}
lm.fit3=lm(mpg~poly(horsepower,3), data=Auto, subset=train)
mean((mpg-predict(lm.fit3,Auto))[-train]^2)
```

8. do it all again with a different seed

```{r}
set.seed(2)
train=sample(392,196) 
lm.fit=lm(mpg~horsepower, data=Auto, subset=train)
mean((mpg-predict(lm.fit,Auto))[-train]^2)
```

```{r}
lm.fit2=lm(mpg~poly(horsepower,2), data=Auto, subset=train)
mean((mpg-predict(lm.fit2,Auto))[-train]^2)
```

```{r}
lm.fit3=lm(mpg~poly(horsepower,3), data=Auto, subset=train)
mean((mpg-predict(lm.fit3,Auto))[-train]^2)
```
### RESULTS:

A model that predicts `mpg` usinga quadratic function of horsepower performs better than a model that involves only a linear function of horsepower. Thereis little evidence in favor of a model that uses a cubic function of horsepower.


FIN.